---
title: "D & I Planning"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny

---

<style type="text/css">

<!-- .navbar { -->
<!--   background-color:lightgreen; -->
<!--   border-color:black; -->
<!-- } -->


body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 13px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

<!-- <style>                      -->
<!-- .navbar { -->
<!--   background-color:crimson; -->
<!--   border-color:black; -->
<!-- } -->
<!-- .navbar-brand { -->
<!-- color:black!important; -->
<!-- } -->


<!-- </style>   -->

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(shinyWidgets)
library(shinyjs)
library(ggthemes)
library(RColorBrewer)
library(grid)
library(DiagrammeR)


# Core
library(tidyverse)
library(tidyquant)
library(gtools)

# Interactive Visualizations
library(plotly)

# Time Series
library(timetk)

# load custom functions
source('..\\01_scripts\\99_functions.R')
```

```{r}
### fabricate data

set.seed(15) 
lengthOut<-12

busASupplySlope<-20
busBSupplySlope<-25
busCSupplySlope<-10

busA<-makeHist("2018",lengthOut,400,950)
busB<-makeHist("2018",lengthOut,1010,1350)
busC<-makeHist("2018",lengthOut,1580,1670)

busAGrowth<-50
busBGrowth<-5
busCGrowth<-10

busALeaderRatio<-15
busBLeaderRatio<-10
busCLeaderRatio<-12

busAHireRate<-35
busBHireRate<-55
busCHireRate<-45

busAPromRate<-15
busBPromRate<-25
busCPromRate<-20


```


Sidebar {.sidebar}
=======================================================================

Projected Demand {data-height=600}
-----------------------------------------------------------------------




### Business A
```{r}
useShinyjs(rmd = TRUE)

numericInputIcon(
  inputId = "busAGrowth",
  label   = h4(""),
  value = busAGrowth,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business B
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busBGrowth",
  label   = h4(""),
  value = busBGrowth,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business C
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busCGrowth",
  label   = h4(""),
  value = busCGrowth,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

```{r}
actionButton(inputId = "resetGrowth", label = "Reset", color='grey')

observeEvent(eventExpr = input$resetGrowth, handlerExpr = {
  
  updateNumericInput(
   inputId = "busAGrowth",
   value = busAGrowth)
  
  updateNumericInput(
   inputId = "busBGrowth",
   value = busBGrowth)
    
  updateNumericInput(
   inputId = "busCGrowth",
   value = busCGrowth)
  
})
```



Leader Ratio {data-height=600}
-----------------------------------------------------------------------

### Business A
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busALeaderRatio",
  label   = h4(""),
  value = busALeaderRatio,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business B
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busBLeaderRatio",
  label   = h4(""),
  value = busBLeaderRatio,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business C
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busCLeaderRatio",
  label   = h4(""),
  value = busCLeaderRatio,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

```{r}
actionButton(inputId = "resetPyramid", label = "Reset", color='grey')

observeEvent(eventExpr = input$resetPyramid, handlerExpr = {
  
  updateNumericInput(
   inputId = "busALeaderRatio",
   value = busALeaderRatio)
  
  updateNumericInput(
   inputId = "busBLeaderRatio",
   value = busBLeaderRatio)
    
  updateNumericInput(
   inputId = "busCLeaderRatio",
   value = busCLeaderRatio)
  
})
```


Female Promotions {data-height=600}
-----------------------------------------------------------------------

### Business A
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busAFemPromotions",
  label   = h4(""),
  value = busAPromRate,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business B
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busBFemPromotions",
  label   = h4(""),
  value = busBPromRate,
  min = -100,
  max = 500,
  icon = icon("percent"))
```


### Business C
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busCFemPromotions",
  label   = h4(""),
  value = busCPromRate,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

```{r}
actionButton(inputId = "resetPromotions", label = "Reset", color='grey')

observeEvent(eventExpr = input$resetPromotions, handlerExpr = {
  
  updateNumericInput(
   inputId = "busAFemPromotions",
   value = busAPromRate)
  
  updateNumericInput(
   inputId = "busBFemPromotions",
   value = busBPromRate)
    
  updateNumericInput(
   inputId = "busCFemPromotions",
   value = busCPromRate)
  
})
```

Female New Hires {data-height=600}
-----------------------------------------------------------------------

### Business A
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busAFemHires",
  label   = h4(""),
  value = busAHireRate,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business B
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busBFemHires",
  label   = h4(""),
  value = busBHireRate,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

### Business C
```{r}
useShinyjs(rmd = TRUE)
numericInputIcon(
  inputId = "busCFemHires",
  label   = h4(""),
  value = busCHireRate,
  min = -100,
  max = 500,
  icon = icon("percent"))
```

```{r}
actionButton(inputId = "resetHires", label = "Reset", color='grey')

observeEvent(eventExpr = input$resetHires, handlerExpr = {
  
  updateNumericInput(
   inputId = "busAFemHires",
   value = busAGrowth)
  
  updateNumericInput(
   inputId = "busBFemHires",
   value = busBGrowth)
    
  updateNumericInput(
   inputId = "busCFemHires",
   value = busCGrowth)
  
})
```


Overview
=======================================================================

Column {data-height=400}
-----------------------------------------------------------------------

### D & I Drivers
```{r}
grViz(diagram = "digraph flowchart {
      # define node aesthetics
      node [fontname = Arial, shape = oval, color = '#A8DDB5', style = filled, fontcolor = White]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      node [fontname = Arial, shape = rectangle, color = '#74ADD1', style = filled, fontcolor = White]
      tab3 [label = '@@3']
      tab7 [label = '@@7']

# set up node layout
      tab1 -> tab3;
      tab2 -> tab3;
      tab3 -> tab4;
      tab3 -> tab5;
      tab3 -> tab6;
      tab4 -> tab7;
      tab5 -> tab7;
      tab6 -> tab7;
      
      }
      [1]: 'Projected Attrition'
      [2]: 'Projected Demand'
      [3]: 'Projected Talent Gaps'
      [4]: 'Hiring Patterns'
      [5]: 'Promotions / Mobility Patterns'
      [6]: 'Pyramid Constraints'
      [7]: 'Projected Organizational Diversity'
      ")
```




Diversity Targets
=======================================================================

Column {data-height=400}
-----------------------------------------------------------------------

### Gender Representation, Current and Target
```{r}
targetMgr<-.25
targetStaff<-.4

diversity2<-reactive(diversity() %>%
                       mutate(countPect=ifelse(gender=='Female' & period=='forecast' & mgr=='Manager',targetMgr,countPect)) %>%
                       mutate(countPect=ifelse(gender=='Male' & period=='forecast' & mgr=='Manager',1-targetMgr,countPect)) %>%
                       mutate(countPect=ifelse(gender=='Female' & period=='forecast' & mgr=='Individual Contributor',targetStaff,countPect)) %>%
                       mutate(countPect=ifelse(gender=='Male' & period=='forecast' & mgr=='Individual Contributor',1-targetStaff,countPect)) %>%
  group_by(mgr,period) %>%
  mutate(label_y = cumsum(countPect) - 0.5 * countPect)
)

colors1<-c("#9970AB","#5AAE61")
myColors<-colors1
names(myColors) <- c('Male','Female')

percent <- function(x, digits = 1, format = "f", ...) {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}

renderPlot({ggplot(diversity2(),aes(x = period, y = countPect, fill=gender)) +
  geom_bar(stat='identity') +
  scale_fill_manual(values=myColors) +
  coord_flip() +
  facet_grid(. ~ mgr) +
  scale_y_continuous("",labels = scales::percent_format()) +
  scale_x_discrete('',labels=c('Target \n (2023 Year End)','Current \n (2020 Year End)')) +
  #labs(title = 'Female vs. Male as % of Total Headcount, Current and Projected') +
  #theme(plot.title = element_text(hjust = 0.5)) +
  theme_fivethirtyeight() +
  theme(legend.title = element_blank()) +
  geom_text(aes(y = label_y, label = percent(countPect)), colour = "black")
})
```

Diversity Projections
=======================================================================

Column {data-height=400}
-----------------------------------------------------------------------

### Gender Representation, Current and Projected
```{r}
orgWideMgrRatio<-.35
orgWideFemStaffPect<-.343
orgWideFemMgrPect<-.12
orgWidePopulation<-busA$headcount[busA$date==max(busA$date)]+busB$headcount[busB$date==max(busB$date)]+busC$headcount[busC$date==max(busC$date)]

orgWideMgrs<-round(orgWideMgrRatio*orgWidePopulation,0)
orgWideFemMgrs<-round(orgWideFemMgrPect*orgWideMgrs,0)
orgWideMaleMgrs<-orgWideMgrs-orgWideFemMgrs
orgWideStaff<-round(orgWidePopulation-orgWideMgrs,0)
orgWideFemStaff<-round(orgWideFemStaffPect*orgWideStaff,0)
orgWideMaleStaff<-orgWideStaff-orgWideFemStaff

supply<-reactive(busAForecast()$forecastSupply[busAForecast()$date==max(busAForecast()$date)] + 
                  busBForecast()$forecastSupply[busBForecast()$date==max(busBForecast()$date)] +
                  busCForecast()$forecastSupply[busCForecast()$date==max(busCForecast()$date)])

lostSupply<-reactive(orgWidePopulation-supply())

lostFemMgrs<-reactive(orgWideFemMgrs/orgWidePopulation*lostSupply())
lostMaleMgrs<-reactive(orgWideMaleMgrs/orgWidePopulation*lostSupply())
lostFemStaff<-reactive(orgWideFemStaff/orgWidePopulation*lostSupply())
lostMaleStaff<-reactive(orgWideMaleStaff/orgWidePopulation*lostSupply())

orgWideFemMgrsNew<-reactive(orgWideFemMgrs-lostFemMgrs()+newFemMgrsA()+newFemMgrsB()+newFemMgrsC())
orgWideMaleMgrsNew<-reactive(orgWideMaleMgrs-lostMaleMgrs()+newMgrsA()+newMgrsB()+newMgrsC()-newFemMgrsA()-newFemMgrsB()-newFemMgrsC())
orgWideFemStaffNew<-reactive(orgWideFemStaff-lostFemStaff()+newFemStaffA()+newFemStaffB()+newFemStaffC())
orgWideMaleStaffNew<-reactive(orgWideMaleStaff-lostMaleStaff()+newStaffA()+newStaffB()+newStaffC()-newFemStaffA()-newFemStaffB()-newFemStaffC())


diversity<-reactive(data.frame
(
  period=c(rep('prevYear',4),rep('forecast',4)),
  gender=rep(c('Female','Female','Male','Male'),2),
  mgr=rep(c('Manager','Individual Contributor'),4),
  count=c(orgWideFemMgrs,orgWideFemStaff,orgWideMaleMgrs,orgWideMaleStaff,orgWideFemMgrsNew(),orgWideFemStaffNew(),orgWideMaleMgrsNew(),orgWideMaleStaffNew())
)  %>%
  mutate(gender=as.factor(gender)) %>%
  mutate(gender=relevel(gender, "Male")) %>%
  group_by(period,mgr) %>%
  mutate(total=sum(count)) %>%
  ungroup() %>%
  mutate(countPect=round(count/total,3)) %>%
  group_by(mgr,period) %>%
  mutate(label_y = cumsum(countPect) - 0.5 * countPect)
)


orgHeadcountNew<-reactive(orgWidePopulation-lostSupply()+newMgrsA()+newStaffA()+newMgrsB()+newStaffB()+newMgrsC()+newStaffC())

totalGaps<-reactive(gapA()+gapB()+gapC())

```

```{r}

colors1<-c("#9970AB","#5AAE61")
colors1<-c("#80CDC1","#B8E186")
colors1<-c("#CCEBC5","#74ADD1")



myColors<-colors1
names(myColors) <- c('Male','Female')

percent <- function(x, digits = 1, format = "f", ...) {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}

#ggplot(diversity,aes(x = period, y = countPect, fill=forcats::fct_rev(gender))) +
renderPlot({ggplot(diversity(),aes(x = period, y = countPect, fill=gender)) +
  geom_bar(stat='identity') +
  scale_fill_manual(values=myColors) +
  coord_flip() +
  facet_grid(. ~ mgr) +
  scale_y_continuous("",labels = scales::percent_format()) +
  scale_x_discrete('',labels=c('Projected \n (2023 Year End)','Current \n (2020 Year End)')) +
  #labs(title = 'Female vs. Male as % of Total Headcount, Current and Projected') +
  #theme(plot.title = element_text(hjust = 0.5)) +
  theme_fivethirtyeight() +
  theme(legend.title = element_blank()) +
  geom_text(aes(y = label_y, label = percent(countPect)), colour = "black")
})
  
#renderDataTable({diversity()})
#renderPlot()

```




Column {data-height=150}
-----------------------------------------------------------------------

### Business A
```{r}
### create forecasts based on bus-level data and inputs
busAForecast <- reactive({makeForecast(busA,"2021",lengthOut,input$busAGrowth,busASupplySlope)})
renderPlot({makePlot(busAForecast())})
```

### Business B
```{r}
### create forecasts based on bus-level data and inputs
busBForecast <- reactive({makeForecast(busB,"2021",lengthOut,input$busBGrowth,busBSupplySlope)})
renderPlot({makePlot(busBForecast())})
```

### Business C
```{r}
### create forecasts based on bus-level data and inputs
busCForecast <- reactive({makeForecast(busC,"2021",lengthOut,input$busCGrowth,busCSupplySlope)})
renderPlot({makePlot(busCForecast())})
```

Column {data-height=200}
-----------------------------------------------------------------------

### Gaps
```{r}
gapA<-reactive(busAForecast()$forecast[busAForecast()$date==max(busAForecast()$date)]-busAForecast()$forecastSupply[busAForecast()$date==max(busAForecast()$date)])
newMgrsA<-reactive(round(input$busALeaderRatio*gapA()/100,0))
newStaffA<-reactive(gapA()-round(input$busALeaderRatio*gapA()/100,0))
newFemMgrsA<-reactive(round(input$busAFemPromotions*newMgrsA()/100,0))
newFemStaffA<-reactive(round(input$busAFemHires*newStaffA()/100,0))


htmlOutput("openingsA")
  output$openingsA <- renderUI({
    HTML(paste("Overall: ", gapA(), "<br/>", 
               "Managers: ", newMgrsA(), "<br/>",
               "Individual Contributor: ", newStaffA(), "<br/>",
               "<br/>",
               "New Female Managers: ","<br/>" ,
               input$busAFemPromotions/100, " X ", newMgrsA(), " = ",  newFemMgrsA(),"<br/>" ,"<br/>",
               "New Female Individual Contributors: ","<br/>" ,
               input$busAFemHires/100, " X ", newStaffA(), " = ",  newFemStaffA(),
               sep=''))
  })
```

### Gaps
```{r}
gapB<-reactive(busBForecast()$forecast[busBForecast()$date==max(busBForecast()$date)]-busBForecast()$forecastSupply[busBForecast()$date==max(busBForecast()$date)])
newMgrsB<-reactive(round(input$busBLeaderRatio*gapB()/100,0))
newStaffB<-reactive(gapB()-round(input$busBLeaderRatio*gapB()/100,0))
newFemMgrsB<-reactive(round(input$busBFemPromotions*newMgrsB()/100,0))
newFemStaffB<-reactive(round(input$busBFemHires*newStaffB()/100,0))


htmlOutput("openingsB")
  output$openingsB <- renderUI({
    HTML(paste("Overall: ", gapB(), "<br/>", 
               "Managers: ", newMgrsB(), "<br/>",
               "Individual Contributor: ", gapB()-round(input$busBLeaderRatio*gapB()/100,0), "<br/>",
               "<br/>",
               "New Female Managers: ","<br/>" ,
               input$busBFemPromotions/100, " X ", newMgrsB(), " = ",  newFemMgrsB(),"<br/>","<br/>",
               "New Female Individual Contributors: ","<br/>" ,
               input$busBFemHires/100, " X ", newStaffB(), " = ",  newFemStaffB(),
               sep=''))
  })
```

### Gaps
```{r}
gapC<-reactive(busCForecast()$forecast[busCForecast()$date==max(busCForecast()$date)]-busCForecast()$forecastSupply[busCForecast()$date==max(busCForecast()$date)])
newMgrsC<-reactive(round(input$busCLeaderRatio*gapC()/100,0))
newStaffC<-reactive(gapC()-round(input$busCLeaderRatio*gapC()/100,0))
newFemMgrsC<-reactive(round(input$busCFemPromotions*newMgrsC()/100,0))
newFemStaffC<-reactive(round(input$busCFemHires*newStaffC()/100,0))


htmlOutput("openingsC")
  output$openingsC <- renderUI({
    HTML(paste("Overall: ", gapC(), "<br/>", 
               "Managers: ", newMgrsC(), "<br/>",
               "Individual Contributor: ", gapC()-round(input$busCLeaderRatio*gapC()/100,0), "<br/>",
               "<br/>",
               "New Female Managers: ","<br/>" ,
               input$busCFemPromotions/100, " X ", newMgrsC(), " = ",  newFemMgrsC(),"<br/>","<br/>",
               "New Female Individual Contributors: ","<br/>" ,
               input$busCFemHires/100, " X ", newStaffC(), " = ",  newFemStaffC(),
               sep=''))
  })
```



Hiring and Mobility
=======================================================================

Column {data-height=400}
-----------------------------------------------------------------------

```{r}
hiring<-data.frame(Business=c('Business A','Business B','Business C'),
                   pectFemale=c(35,48,46),
                   pectFemaleHires=c(busAHireRate,busBHireRate,busCHireRate))

promotions<-data.frame(Business=c('Business A','Business B','Business C'),
                   pectFemaleEligible=c(25,20,35),
                   pectFemalePromotions=c(busAPromRate,busBPromRate,busCPromRate))
```


### Hiring
```{r}
ggplot(hiring, aes(x=pectFemale, y=pectFemaleHires)) + 
  geom_point(color="#FDAE6B",size=12) +
  #scale_size_continuous(range=c(2,12)) +
  geom_label(aes(label = Business)) +
  scale_x_continuous('Female Headcount as % of Total Headcount', limits=c(0,100)) +
  scale_y_continuous('Female Hiring as % of Total Hiring', limits=c(0,100)) +
  labs(title="Female Representation vs. Hires", subtitle="Previous Year") +
  geom_abline(slope=1)
```


### Promotions
```{r}
ggplot(promotions, aes(x=pectFemaleEligible, y=pectFemalePromotions)) + 
  geom_point(color="#FDAE6B",size=12) +
  #scale_size_continuous(range=c(2,12)) +
  geom_label(aes(label = Business)) +
  scale_x_continuous('Female Eligible Population as % of Total Eligible Population', limits=c(0,100)) +
  scale_y_continuous('Female Promotions as % of Total Promotions', limits=c(0,100)) +
  labs(title="Female Promotions vs. Eligibility", subtitle="Previous Year") +
  geom_abline(slope=1)
```






